Universal Anonymous Signatures

### 2022-08-17 prism-backend/research/gsac/formal-uas.tex
Applying changes after pass.

\jesus{Adding a \uid into \HU or \CU within an oracle that is executed by end
  users in the real world is a bit weird if not clarified. Some arguments may
  be possible.}

@@

Next we formalize our notion of Universal Anonymous Signatures
(\UAS). We define its syntax, model, and give a generic construction, which
we prove secure according to our model.

The main contribution of this section is giving a simple syntax and model that
still allow spanning a wide variety of related schemes. We combine aspects of GS
and AC schemes, generalizing whenever possible. Like in ACs, there are multiple
issuers, and each user can get one or more credentials from any of them; and,
also, use more than one credential simultaneously to produce a signature. We
incorporate openers, as in GSs, but there is no tight relationship between
issuer and opener. As a consequence, signers (potentially along with verifiers)
may choose, on a per-signature basis, the policies governing the utility
information extractable from a signature. Finally, we incorporate functions that
allow tweaking the conditions checked at credential issuance and signature
generation times, including the information that an opener will be able to
extract from a signature. This flexibilizes the scheme even beyond the loose
relationship between issuer and opener.

\paragraph{Users and credentials.} %
We model a scheme in which every single user may have multiple credentials.
Moreover, previously obtained credentials can be leveraged simultaneously to
obtain a new one. In this setting, a perhaps too strict assumption we make is
that, once a user gets compromised, all of the credentials owned by that user
are compromised too. While there may be real world situations for which this is
too aggressive, it is certainly a worst-case scenario, and greatly simplifies
the modelling.
%
Somehow related, we model a scheme in which users generate their secret keys in
a standalone way, and then leverage their keys to request credentials.
Therefore, if one ``user'' generates (e.g.) two keys, and then uses each of
these keys to request multiple credentials, then from the point of view of our
modelling, we see this \emph{cryptographically} as two different users.

\todo{Clarify that, for us, issuers and users are essentially the same thing.}

@@

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$\KeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, a user runs
  \KeyGen to generate its user key pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\ISet(\upk,\usk,\fissue) \rightarrow \ipk$.] Given a user key
  pair, and an issuance function \fissue for checking that credential requestors
  meet some conditions to be issued a credential, an existing user runs \ISet to
  extend the user public key, enabling this user to issue credentials meeting
  \fissue.
%\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
%  key pair.
\item[$\langle
  \Obtain(\usk,\cidu,\ipk,\sCred,\attrs),
  \Issue(\isk,\cidi,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,R/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the \Obtain
  process, receive a credential $\Cred=(\cid,\attrs,\cred,\ipk)$
  from an issuer in the system. $\cid=(\cidi,\cidu)$ is a unique identifier for
  the credential, where issuer and user randomly pick \cidi and \cidu,
  respectively (to ease notation, whenever we write just \cid, we mean $(\cidi,
  \cidu)$). \ipk is the issuer's public key and \cred is the actual credential,
  on attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i=(\cidi_i,\cidu_i),\cattrs_i,\cred_i,
  \ipk_i)\rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for
  readability. The user outputs the produced credential \Cred, while the issuer
  outputs $R \gets (\yissue,\utrans)$, for some value $\yissue$ output by
  the \fissue defined by the issuer, and $\utrans$ being the transcript of
  the communication.
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \sCred, a message \msg and evaluation function \feval, returns
  signature \sig, and a plaintext value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials issued by the issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

\paragraph{Issuance, evaluation, and opening functions.} %
We introduce three functions in our syntax and model. Through them,
it is possible to modulate the behaviour of the resulting instantiation, by
controling the conditions upon which a new credential can be issued, or the
information revealed at signing time, or after signing. In all cases, it is
the user who computes them, and has to prove correctness of such computation.
We give concrete examples in \secref{sec:relationships}, and define them next:

\begin{description}
\item[$\fissue: (\upk,\usk,\lbrace (\cid_i,\cattrs_i)\rbrace_{i \in [n]},\attrs)
  \rightarrow \yissue$.] Chosen
  by each issuer within a family of functions \famfissue, the issuance function
  defines the customized conditions required by the issuer to grant a credential
  over attributes \attrs, when requested by a user with key pair $(\upk,\usk)$,
  leveraging a set of $n$ previously obtained credentials with identifiers and
  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where
  $n$ may be $0$ if no previously obtained credential is used). \fissue returns
  a value $\yissue \in \rngfissue \cup \lbrace 0 \rbrace$, where we adopt the
  convention that $\yissue = 0$ means that the issuance request is denied.
  \fissue functions must be \UAS-acceptable, as defined in
  \defref{def:uas-acc-func}.
\item[$\feval: (\upk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user public key \upk, a set of credentials with identifiers
  and attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$
  (where $n \ge 1$), and the message to be signed \msg. \feval outputs two
  values, $\yeval^0$ and $\yeval^1$. $\yeval^0$ is output directly alongside the
  signature,  both can in addition be used to modulate the behaviour of
  \finsp, and must belong in a well defined set \rngfeval. For readability,
  we write $\Yeval = (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\upk,\lbrace \cid_i,\cattrs_i\rbrace_{i \in [n]},
  \msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value (derived from the user's secret key,
  credentials' identifiers and attributes used for signing, and signed message)
  should be extractable by an opener. Its behaviour can be modulated by \Yeval,
  and it outputs a value \yinsp, which must belong in a well defined set
  \rngfinsp.
\end{description}

@@

\begin{figure}[ht!]
  \centering  
  \scalebox{0.9}{
    \procedure{$\Exp^{\UAS-acc-b}_\adv(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\upk,\usk) \gets \KeyGen(\parm) \\
      (\st,\attrs, \lbrace (\cidi,\cidu,\cattrs_i) \rbrace_{i\in[n]})
      \gets \adv(\upk) \\
      \pcif b=0:
      \yissue^* \gets \fissue(\upk,\usk,\lbrace (\cidi,\cattrs_i)
      \rbrace_{i\in[n]},\attrs) \\
      \pcelse: \yissue^* \getr \rngfissue \setminus \lbrace 0 \rbrace \\
      b^* \gets \adv(\st,\yissue^*) \\
      \pcreturn b^*
    }
  }
  \label{fig:uas-acceptable}
  \caption{Formal definition of \UAS-acceptable \fissue functions.}
\end{figure}

\begin{definition}{(\UAS-acceptable \fissue functions)}
  \label{def:uas-acc-func}
  A \fissue function is \UAS acceptable if, for any p.p.t. adversary \adv,
  $|\Pr[\Exp^{\UAS-acc-1}_\adv(1^\secpar)=1]-\Pr[\Exp^{\UAS-acc-0}_\adv
  (1^\secpar)=0]|$ is a negligible function of $1^\secpar$.
\end{definition}

A \UAS construction thus can only be secure if the \fissue function it uses is
\UAS-acceptable.
%
Next, we define the concept of \CUASGen restrictions. Briefly, these are special
cases of our generic construction that target a concrete variant of the
utility-privacy tradeoff by defining concrete \fissue, \feval and \finsp
functions. Security of \CUASGen implies security of its restrictions, as long as
the chosen functions are \CUASGen-acceptable.

@@

We define the security expected from an \UAS scheme using a game-based approach.
An \UAS scheme must ensure privacy at credential issuance, meaning that two
runs of the credential issuance protocol should not leak any information beyond
necessary about the user requesting the credential. Note that this is now
crucial for privacy since, as AC schemes, \UAS allows multiple credentials per
user -- thus, knowing what user is requesting which credential can lead to user
profiling. It must also ensure signature privacy, meaning that no information
can be learned by third parties from a signature, beyond what the user chooses
to reveal, and what may be extractable by the chosen opener. Issuance
unforgeability requires that \UAS schemes ensure that the claims used to support
a credential request cannot be falsified (issuance unforgeability). Similarly,
signature unforgeability requires that no adversary should be able to falsify
the correctness proofs for the claims included in the signatures. In both cases
(issuance and signature unforgeability), we require all credentials involved in
the corresponding process to be associated to a known user key. Finally, \UAS
schemes inherit the useful non-frameability property of GS schemes where even
the issuer is corrupt. In this case, we can ensure that no honest user
can be framed with having created a signature that s/he did not create --
although the concept may get a bit blurred, as there is no traditional opening.
%
We describe next the global variables and oracles that we use in our modelling.

\paragraph{Global Variables.} %
\todo{Clarify that {\iid}s are just {\uid}s.}
Users are referred to with user identifiers, \uid; for credentials, we use \cid;
for issuers, \iid; and for openers, \oid.  In all cases, we use bold font to
denote sets: e.g., \scid and \siid denote sets of credential and issuer
identifiers. All tables/sets are initialized as empty tables/sets. For
notational convenience, we often use these identifiers instead of the
corresponding user/issuer/opener keys.

\begin{description}
\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of honest users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.
\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of corrupt users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.    
\item[\UK, \PUBUK and \PRVUK.] \UK maintains user key pairs $(\upk,\usk)$. To
  refer to the key of a specific user, we use $\UK[\uid]$. \PUBUK indexes the
  public keys, and \PRVUK the private keys.
\item[\IK, \PUBIK and \PRVIK.] \IK maintains issuer key pairs, where
  $\IK[\iid]$ refers to the key pair of the issuer with identifier \iid. We
  use \PUBIK to refer to the public component, which also includes the \fissue
  function; and \PRVIK refers to the private component of the key pair.
\item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for opener key pairs. Instead
  of \fissue, \OK includes the \finsp function.
\item[\CRED.] Stores information related to credentials obtained by users in
  the system. Thus, it is indexable by \cid. More specifically, it stores
  tuples of the form $(\uid,\cred,\iid,\attrs,n,\lbrace (\cid_i,\iid_i)
  \rbrace_{i \in [n]})$, where \uid is the identifier of the owner of the
  credential, \cred (when available) is the credential itself, \iid is the
  identifier of the credential issuer, \attrs are the attributes included in
  \cred, $n$ is the number of credentials used to support this request, and
  $(\cid_i,\iid_i)$ for $i \in [n]$ are the corresponding credential and issuer
  identifiers. For notational convenience, we may use $\CRED[\scid]$
  to refer to $\CRED[\cid]$ for all {\cid}s in a set \scid. Also, when clear
  from context, we sometimes use $\CRED[\cid]$ (resp. $\CRED[\scid]$ to
  mean \cred (resp. \scred) in $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,
  \cdot,\cdot)$ (resp. $\CRED[\scid]$).
\item[\CCRED.] Like \CRED, but keeps track of challenge credentials in the
  issuance anonymity game.
\item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
  ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$'', or
  $\bot$ if there is no wuch \uid. We may also use \OWNR over a set of {\cid}s
  (\scid). In that case, our convention is that $\OWNR[\scid]$ returns $\bot$ if
  not all passed {\cid}s belong to the same \uid. Since $\bot$ is not a valid
  \uid, all conditions checking membership of the output of \OWNR to a list of
  users equal false if \OWNR returns $\bot$.
\item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
  ``\attrs such that $\CRED[\cid] = (\cdot,\cdot,\cdot,\attrs,\cdot,\cdot)$''.
\item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
  ``\iid such that $\CRED[\cid] = (\cdot,\cdot,\iid,\cdot,\cdot,\cdot)$''.
\item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
  this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
  the opener, \scid is the set of identifiers of the credentials used for
  signing, \feval is the signing evaluation function, and \sig and \msg are the
  produced signature and signed message.
\item[\CSIG.] Maintains challenge signatures output to the adversary in the
  signature anonymity game, and is indexable by challenge signatures \csig.
  Each entry contains also $\cuid_b$ and $\cscid_b$, respectively the challenge
  user  and credential identifiers set used to produce \csig; as well as the
  corresponding challenge user and credential set indexed by the complementary
  $1-b$; the signed message \msg and signing evaluation function \feval, the
  result of \feval, \Yeval, and the opener identifier \oid.
\end{description}

@@

\begin{description}
% \item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
%   the associated issuance function.
\item[\HUGEN.] Adds a new honest user to the game, generating its keypair.
\item[\HUGEN.] Adds a new corrupt user to the game, setting its \upk to the
  value given by the adversary.  
\item[\OGEN.] Adds a new opener to the game, generating its key pair and
  setting the associated evaluation and inspection functions.
% \item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
%   key to the adversary.
\item[\ISET.] ``Upgrades'' an user to become an issuer, specifying its
  associated issuance function.
\item[\UCORR.] Corrupts an existing (and honest) user, by giving its secret
  key to the adversary. If the user was also an issuer, it becomes a corrupt
  issuer too.
\item[\OCORR.] Corrupts an existing (and honest) opener, by giving its secret
  key to the adversary.
% \item[\HUGEN.] Adds a new honest user to the game, by honestly generating
%   the user's key pair.
% \item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
%   user already exists and is honest, corrupts it, leaking its key and
%   credentials.
\item[\RREG.] Reads the given transcript table entry.
\item[\WREG.] Sets a transcript table entry to the given value.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer, by
  letting it interact with honest users who want to receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures from credentials belonging
  to honest users.
\item[\OPEN.] Given an honestly produced signature, outputs the result of the
  opening function, along with a correctness proof.
\item[\OBTCHALb.] Upon receiving a target credential identifier, two challenge
  users and credential sets, an honest issuer identifier, and a set of
  attributes, issues a credential for the challenge user and credential set
  defined by the bit $b$. 
\item[\CHALb.] Upon receiving two challenge users and credential sets, a common
  singing evaluation function and a message, returns a signature produced by one
  of these two user and credential sets, defined by the bit $b$.
\end{description}

>>>>

@@

Next we formalize our notion of Universal Anonymous Signatures
(\UAS). We define its syntax, model, and give a generic construction, which
we prove secure.

The main contribution of this section is giving a simple syntax and model that
still allow spanning a wide variety of related schemes. We combine aspects of GS
and AC schemes, generalizing whenever possible. Like in ACs, there are multiple
issuers, and each user can get one or more credentials from any of them; and,
also, use more than one credential simultaneously to produce a signature. We
incorporate openers, as in GSs, but there is no tight relationship between
issuer and opener. As a consequence, signers (potentially along with verifiers)
may choose, on a per-signature basis, the policies governing the utility
information extractable from a signature. Finally, we incorporate functions that
allow tweaking the conditions checked at credential issuance and signature
generation times, including the information that an opener will be able to
extract from a signature.

\paragraph{Users and credentials.} %
We model a scheme in which every single user may have multiple credentials.
Moreover, previously obtained credentials can be leveraged simultaneously to
obtain a new one. In this setting, a perhaps too strict assumption we make is
that, once a user gets compromised, all of the credentials owned by that user
are compromised too. While there may be real world situations for which this is
too aggressive, it is certainly a worst-case scenario, and greatly simplifies
the modelling.
%
Somehow related, we model a scheme in which users generate their secret keys in
a standalone way, and then leverage their keys to request credentials.
Therefore, if one ``user'' generates (e.g.) two keys, and then uses each of
these keys to request multiple credentials, then from the point of view of our
modelling, we see this \emph{cryptographically} as two different users.
This may seem too ideal to model real world situations. However, we argue that
this can in fact be very close to reality, where a well-known issuer, after
properly identifying a user, attests the (possibly blinded) public key this
user proves control of. Indeed, our model and syntax support exactly this
approach, by allowing users to leverage previously obtained credentials in
order to request new ones.

\paragraph{Users and issuers.} %
Finally, a relevant aspect of our approach is that users and issuers are
essentially the same thing: just an entity with a key pair. The difference is
that, when users wish to become issuers, they have to advertise their public
keys, along with their conditions for granting credentials. For simplicity, we
just assume that they somehow ``publish their public keys''. In practice, this
may be done in several ways, depending on the situation: self-signing, relying
on external PKIs, bulletin-boards, etc.
%
This approach has actually been used before to model delegatable anonymous
credentials \cite{bcc+09}, and it turns out to be also very useful for our
approach to build ring signatures from \UAS.

@@

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions.
\item[$\KeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, a user runs
  \KeyGen to generate its user key pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\ISet(\upk,\usk,\fissue) \rightarrow \ipk$.] Given a user key
  pair, and an issuance function \fissue for checking that credential requestors
  meet some conditions to be issued a credential, an existing user runs \ISet to
  extend the user public key, enabling this user to issue credentials meeting
  \fissue.
%\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
%  key pair.
\item[$\langle
  \Obtain(\usk,\cidu,\ipk,\sCred,\attrs),
  \Issue(\isk,\cidi,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,R/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk receive a credential
  $\Cred=(\cid,\attrs,\cred,\ipk)$
  from an issuer in the system. $\cid=(\cidi,\cidu)$ is a unique identifier for
  the credential, where issuer and user randomly pick \cidi and \cidu,
  respectively (to ease notation, whenever we write just \cid, we mean $(\cidi,
  \cidu)$). \ipk is the issuer's public key and \cred is the actual credential,
  on attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i=(\cidi_i,\cidu_i),\cattrs_i,\cred_i,
  \ipk_i)\rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for
  readability. The user outputs the produced credential \Cred, while the issuer
  outputs $R \gets (\yissue,\utrans)$, for some value $\yissue$ output by
  the \fissue function defined by the issuer, and $\utrans$ being the transcript
  of the communication.
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \sCred, a message \msg and evaluation function \feval, returns
  signature \sig, and a plaintext value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials by issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

\paragraph{Issuance, evaluation, and opening functions.} %
We introduce three functions in our syntax and model. Through them,
it is possible to modulate the behaviour of the resulting instantiation, by
controling the conditions upon which a new credential can be issued, the
information revealed at signing time, or after signing. In all cases, it is
the user who computes them, and has to prove correctness of such computation.
We give concrete examples in \secref{sec:relationships}, and define them next:

\begin{description}
\item[$\fissue: (\upk,\lbrace (\cid_i,\cattrs_i)\rbrace_{i \in [n]},\attrs)
  \rightarrow \yissue$.] Chosen
  by each issuer within a family of functions \famfissue, the issuance function
  defines the customized conditions required by the issuer to grant a credential
  over attributes \attrs, when requested by a user with public key \upk,
  leveraging a set of $n$ previously obtained credentials with identifiers and
  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where
  $n$ may be $0$ if no previously obtained credential is used). \fissue returns
  a value $\yissue \in \rngfissue \cup \lbrace 0 \rbrace$, where we adopt the
  convention that $\yissue = 0$ means that the issuance request is denied.
  \fissue functions must be \UAS-acceptable, as defined in
  \defref{def:uas-acc-func}.
\item[$\feval: (\upk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user public key \upk, a set of credentials with identifiers
  and attributes $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$
  (where $n \ge 1$), and the message to be signed \msg. \feval outputs two
  values, $\yeval^0$ and $\yeval^1$. $\yeval^0$ is output directly alongside the
  signature,  both can in addition be used to modulate the behaviour of
  \finsp, and must belong in a well defined set \rngfeval. For readability,
  we write $\Yeval = (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\upk,\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]},
  \msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value (derived from the user's secret key,
  credentials' identifiers and attributes used for signing, and signed message)
  should be extractable by an opener. Its behaviour can be modulated by \Yeval,
  and it outputs a value \yinsp, which must belong in a well defined set
  \rngfinsp.
\end{description}

@@

\begin{figure}[ht!]
  \centering  
  \scalebox{0.9}{
    \procedure{$\Exp^{\UAS-acc-b}_\adv(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\upk,\usk) \gets \KeyGen(\parm) \\
      (\st,\attrs, \lbrace (\cidi,\cidu,\cattrs_i) \rbrace_{i\in[n]})
      \gets \adv(\upk) \\
      \pcif b=0:
      \yissue^* \gets \fissue(\upk,\lbrace (\cidi,\cattrs_i)
      \rbrace_{i\in[n]},\attrs) \\
      \pcelse: \yissue^* \getr \rngfissue \setminus \lbrace 0 \rbrace \\
      b^* \gets \adv(\st,\yissue^*) \\
      \pcreturn b^*
    }
  }
  \label{fig:uas-acceptable}
  \caption{Formal definition of \UAS-acceptable \fissue functions.}
\end{figure}

\begin{definition}{(\UAS-acceptable \fissue functions)}
  \label{def:uas-acc-func}
  A \fissue function is \UAS-acceptable if, for any p.p.t. adversary \adv,
  $|\Pr[\Exp^{\UAS-acc-1}_\adv(1^\secpar)=1]-\Pr[\Exp^{\UAS-acc-0}_\adv
  (1^\secpar)=0]|$ is a negligible function of $1^\secpar$.
\end{definition}

A \UAS construction thus can only be secure if the \fissue function it uses is
\UAS-acceptable.
%
Next, we define the concept of \CUASGen restrictions. Briefly, these are special
cases of our generic construction that target a concrete variant of the
utility-privacy tradeoff by defining concrete \fissue, \feval and \finsp
functions. Security of \CUASGen implies security of its restrictions, as long as
the chosen \fissue functions are \CUASGen-acceptable.

@@

We define the security expected from an \UAS scheme using a game-based approach.
An \UAS scheme must ensure privacy at credential issuance, meaning that two
runs of the credential issuance protocol should not leak any information beyond
necessary about the user requesting the credential. Note that this is now
crucial for privacy since \UAS allows multiple credentials per
user -- thus, knowing what user is requesting which credential can lead to user
profiling. It must also ensure signature privacy, meaning that no information
can be learned by third parties from a signature, beyond what the user chooses
to reveal, and what may be extractable by the chosen opener. Unforgeability
requires that \UAS schemes ensure that the claims used to support a credential
request cannot be falsified, and that no adversary is able to falsify
the correctness proofs for the claims included in the signatures. In addition,
we require all credentials involved in the corresponding process to be
associated to a known user key. Finally, \UAS schemes inherit the useful
non-frameability property of GS schemes where even the issuer is corrupt. In
this case, we can ensure that no honest user can be framed with having created a
signature that s/he did not create -- although the concept may get a bit
blurred, as there is no traditional opening.
%
We describe next the global variables and oracles that we use in our modelling.

\paragraph{Global Variables.} %
Users are referred to with user identifiers, \uid; for credentials, we use \cid;
and for openers, \oid. Although issuers are ``extended'' users, and thus can be
identified by their \uid, we also sometimes use \iid to refer to a user acting
as issuer, especially, for operations involving both a user and an issuer (this
also applies for key pairs).
%
All tables/sets are initialized as empty tables/sets. For notational
convenience, we often use these identifiers instead of the corresponding
user/issuer/opener keys.
%
We use the following sets and tables in our definitions:

\begin{description}
\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Sets of
  honest {\uid}s/{\iid}s/{\oid}s.
\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Sets of
  corrupt {\uid}s/{\iid}s/{\oid}s.
\item[\UK,\IK,\OK.] Tables maintaining key pairs of users $(\upk,\usk)$, issuers
  $(\ipk,\isk)$, and openers $(\opk,\osk)$. They are indexable by \uid,
  \iid, and \oid, respectively. Also, issuers' public keys contain their \fissue
  function, and openers' public keys contain their \finsp function.
\item[\PUBUK,\PUBIK,\PUBOK and \PRVUK,\PRVIK,\PRVOK.] Shorthands referring to
  public keys of users, issuers or openers ($\mathsf{PXK}$) or their private
  keys ($\mathsf{SXK}$).
\item[\CRED.] Stores information related to credentials obtained by users in
  the system. Thus, it is indexable by \cid. More specifically, it stores
  tuples of the form $(\uid,\cred,\iid,\attrs,n,\lbrace (\cid_i,\iid_i)
  \rbrace_{i \in [n]})$, where \uid is the identifier of the owner of the
  credential, \cred (when available) is the credential itself, \iid is the
  identifier of the credential issuer, \attrs are the attributes included in
  \cred, $n$ is the number of credentials used to support this request, and
  $(\cid_i,\iid_i)$ for $i \in [n]$ are the corresponding credential and issuer
  identifiers. For notational convenience, we may use $\CRED[\scid]$
  to refer to $\CRED[\cid]$ for all {\cid}s in a set \scid. Also, when clear
  from context, we sometimes use $\CRED[\cid]$ (resp. $\CRED[\scid]$) to
  mean \cred (resp. \scred) in $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,
  \cdot,\cdot)$ (resp. $\CRED[\scid]$).
\item[\CCRED.] Like \CRED, but tracks challenge credentials in the issuance
  anonymity game.
\item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
  ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$'', or
  $\bot$ if there is no wuch \uid. We may also use \OWNR over a set of {\cid}s
  (\scid). In that case, our convention is that $\OWNR[\scid]$ returns $\bot$ if
  not all passed {\cid}s belong to the same \uid. Since $\bot$ is not a valid
  \uid, all conditions checking membership of the output of \OWNR to a list of
  users equal false if \OWNR returns $\bot$.
\item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
  ``\attrs such that $\CRED[\cid] = (\cdot,\cdot,\cdot,\attrs,\cdot,\cdot)$''.
\item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
  ``\iid such that $\CRED[\cid] = (\cdot,\cdot,\iid,\cdot,\cdot,\cdot)$''.
\item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
  this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
  the opener, \scid is the set of identifiers of the credentials used for
  signing, \feval is the signing evaluation function, and \sig and \msg are the
  produced signature and signed message.
\item[\CSIG.] Maintains challenge signatures output to the adversary in the
  signature anonymity game, and is indexable by challenge signatures \csig.
  Each entry contains also $\cuid_b$ and $\cscid_b$, respectively the challenge
  user  and credential identifiers set used to produce \csig; as well as the
  corresponding challenge user and credential set indexed by the complementary
  $1-b$; the signed message \msg and signing evaluation function \feval, the
  result of \feval, \Yeval, and the opener identifier \oid.
\end{description}

@@

\begin{description}
% \item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
%   the associated issuance function.
\item[\HUGEN.] Adds a new honest user to the game, generating its keypair.
\item[\HUGEN.] Adds a new corrupt user to the game, setting its \upk to the
  value given by the adversary.  
\item[\OGEN.] Adds a new opener to the game, generating its key pair and
  setting its evaluation and inspection functions.
% \item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
%   key to the adversary.
\item[\ISET.] ``Upgrades'' an user to become an issuer, specifying its
  \fissue function.
\item[\UCORR.] Corrupts an existing (and honest) user, giving its secret
  key to the adversary. If the user was also an issuer, it becomes a corrupt
  issuer too.
\item[\OCORR.] Corrupts an existing (and honest) opener, by giving its secret
  key to the adversary.
% \item[\HUGEN.] Adds a new honest user to the game, by honestly generating
%   the user's key pair.
% \item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
%   user already exists and is honest, corrupts it, leaking its key and
%   credentials.
\item[\RREG.] Reads the given transcript table entry.
\item[\WREG.] Sets a transcript table entry to the given value.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer, by
  letting it interact with honest users who want to receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures using credentials from honest
  users.
\item[\OPEN.] Given an honestly produced signature, outputs the result of the
  opening function, along with a correctness proof.
\item[\OBTCHALb.] Upon receiving a target credential identifier, two challenge
  users and credential sets, an honest issuer identifier, and a set of
  attributes, issues a credential for the challenge user and credential set
  defined by the bit $b$. 
\item[\CHALb.] Upon receiving two challenge users and credential sets, a common
  singing evaluation function and a message, returns a signature produced by one
  of these two user and credential sets, defined by the bit $b$.
\end{description}

{%\setlength\intextsep{\sep}
  \begin{figure*}[ht!]
    \centering
    \scalebox{0.9}{
